Strings functions analysis

### 2022-08-29 article.tex
more methods added

    \textbf{Swift (48)}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun:, removeSubrange, exponentBitCount:, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.

@@

            String \textbf{cut-end} &  &  &  &  &  & &  &  &  & \\ \hline

>>>>

    \textbf{Swift (48)}: init, isZero, isFinite, isInfinite, isEmpty, count, write, append, reserveCapacity, +, +=, insert, replaceSubrange, remove, removeAll, removeFirst, removeLast, significandWidth, removeLast, exponentBitPattern, removeSubrange, significandBitCoun, removeSubrange, exponentBitCount, removeSubrange, filter, drop, dropFirst, dropLast, popLast, lowercased, uppercased, ==, !=, <, <=, >, >=, elementsEqual, starts, lexicographicallyPrecedes, applying, difference, hasPrefix, hasSuffix, contains, allSatisfy, contains.

@@

            String \textbf{pop-back} &  &  &  &  &  & &  &  &  & \\

            Get string \textbf{as-chars} &  &  &  &  &  & &  &  &  & \\

            Get string \textbf{as-canonical} &  &  &  &  &  & &  &  &  & \\

            Check if \textbf{is-ascii}  &  &  &  &  &  & &  &  &  & \\

            String \textbf{copy} &  &  &  &  &  & &  &  &  & \\

            String \textbf{contains-any} &  &  &  &  &  & &  &  &  & \\

            String \textbf{reserve-capacity} &  &  &  &  &  & &  &  &  & \\

            String \textbf{shrink-to-fit} &  &  &  &  &  & &  &  &  & \\ \hline
